### 2014-08-14 Docs/flowchart/flowchart.tex
fix a typo in the delta Gamma_1 term, and clarify an average

Assuming that $\delta \Gamma_1 \ll \gammabar$, we then have \MarginPar{I think that we include to $\delta \Gamma_1^2$ now}
\begin{equation}
\nablab \cdotb \Ub + \frac{1}{\gammabar p_0} \Ub \cdotb \nablab p_0 = S - \frac{1}{\gammabar p_0} \frac{\partial p_0}{\partial t} +
\frac{\delta \Gamma_1}{\gammabar^2 p_0} \frac{\partial p_0}{\partial t} +
\frac{\delta \Gamma_1}{\gammabar^2 p_0} \Ub \cdotb \nablab p_0 \enskip , \label{eq:gammafull}
\end{equation}
The base state evolution equation is the average of this over a layer
\begin{equation}
\nablab \cdot w_0 \er + \frac{1}{\gammabar p_0} w_0 \er \cdotb \nablab p_0 =
\Sbar - \frac{1}{\gammabar p_0} \frac{\partial p_0}{\partial t} + \overline{
  \left ( \frac{\delta \Gamma_1}{\gammabar^2 p_0} \ut \cdotb \nablab p_0
  \right ) } \enskip .
\end{equation}
Subtracting this from equation (\ref{eq:gammafull}), we have
\begin{equation}
\nablab \cdotb \Ubt + \frac{1}{\gammabar p_0} \Ubt \cdotb \nablab p_0 = S -
\Sbar + \frac{\delta \Gamma_1}{\gammabar^2 p_0} \left (\psi + \Ubt \cdotb
\nablab p_0 \right ) - \overline{ \left ( \frac{\delta \Gamma_1}{\gammabar^2 p_0} \Ubt
\cdotb \nablab p_0 \right ) } \enskip .
\end{equation}

>>>>

Assuming that $\delta \Gamma_1 \ll \gammabar$, we then have \MarginPar{I think that we include to $\delta \Gamma_1^2$ now}
\begin{equation}
\nablab \cdotb \Ub + \frac{1}{\gammabar p_0} \Ub \cdotb \nablab p_0 = S - \frac{1}{\gammabar p_0} \frac{\partial p_0}{\partial t} +
\frac{\delta \Gamma_1}{\gammabar^2 p_0} \frac{\partial p_0}{\partial t} +
\frac{\delta \Gamma_1}{\gammabar^2 p_0} \Ub \cdotb \nablab p_0 \enskip , \label{eq:gammafull}
\end{equation}
The base state evolution equation is the average of this over a layer
\begin{equation}
\nablab \cdot w_0 \er + \frac{1}{\gammabar p_0} w_0 \er \cdotb \nablab p_0 =
\Sbar - \frac{1}{\gammabar p_0} \frac{\partial p_0}{\partial t} + \overline{
  \left ( \frac{\delta \Gamma_1}{\gammabar^2 p_0} \Ubt \cdotb \nablab p_0
  \right ) } \enskip .
\end{equation}
where we see that the $[\delta \Gamma_1/(\Gamma_1^2 p_0)] \partial p_0/\partial t$ terms averages to zero, since the average of $\delta\Gamma_1$ term is zero.
Subtracting this from equation (\ref{eq:gammafull}), we have
\begin{equation}
\nablab \cdotb \Ubt + \frac{1}{\gammabar p_0} \Ubt \cdotb \nablab p_0 = S -
\Sbar + \frac{\delta \Gamma_1}{\gammabar^2 p_0} \left (\psi + \Ubt \cdotb
\nablab p_0 \right ) - \overline{ \left ( \frac{\delta \Gamma_1}{\gammabar^2 p_0} \Ubt
\cdotb \nablab p_0 \right ) } \enskip .
\end{equation}
